---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Welcome to the GitHub page for the 'behaviouR' package
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE, fig.keep='all'}
library(ggpubr)
mainImage <- magick::image_read('/Users/denasmacbook/Desktop/behaviouR/Workflow.png')
(mainImage)

```


## Getting started
To download the package from GitHub enter the following lines of code into R.
```{r, eval = FALSE}
# Install devtools from CRAN
install.packages("devtools")
devtools::install_github("https://github.com/DenaJGibbon/behaviouR")
```

## Accessing R scripts
The full tutorials (include scripts as appendices) can be found here: https://bookdown.org/djc426/behaviouR-R-package-tutorials/.

Links to individual R Scripts can be found here: https://github.com/DenaJGibbon/behaviouRtutorials/tree/master/R%20Scripts%20for%20Labs

## Modifying course materials for instructors
You can find and modify the source code for the tutorials by visiting https://github.com/DenaJGibbon/behaviouRtutorials and downloading a .zip file. See https://bookdown.org/yihui/bookdown/ for information on how to modify the code.
