---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Welcome to the github page for the 'behaviouR' package

## Getting started
To download the package from GitHub enter the following lines of code into R.
```{r, eval = FALSE}
# Install devtools from CRAN
install.packages("devtools")
devtools::install_github("https://github.com/DenaJGibbon/behaviouR")
```

## Accessing R scripts
Links to individual R Scripts can be found here:https://github.com/DenaJGibbon/behaviouRtutorials/tree/master/R%20Scripts%20for%20Labs

The full tutorials (include scripts as appendices) can be found here: https://bookdown.org/djc426/behaviouR-R-package-tutorials/.

## Modifying course materials for instructors
You can find and modify the source code for the tutorials by visiting https://github.com/DenaJGibbon/behaviouRtutorials and downloading a .zip file. See https://bookdown.org/yihui/bookdown/ for information on how to modify the code.
